Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-03-08 manuscript 01/index.qmd
making progress on table 2

noquote(summary$"Neurosurgical Intervention"[1])

odds_ratios <- list(
  "Neurosurgical Intervention" = noquote(summary$"Neurosurgical Intervention"[1]),
  "External Ventricular Drain" = noquote(summary$"External Ventricular Drain"[1]),
  "Tracheostomy" = noquote(summary$"Tracheostomy"[1]),
  "Days of Mechanical Ventilation" = noquote(summary$"Days of Mechanical Ventilation"[1]),
  "DNR Order" = noquote(summary$"DNR Order"[1]),
  "Withdrawal of Life-Sustaining Therapy" = noquote(summary$"Withdrawal of Life-Sustaining Therapy"[1]),
  "Early Withdrawal of Life-Sustaining Therapy" = noquote(summary$"Early Withdrawal of Life-Sustaining Therapy"[1])
)

credible_ints <- list(
  "Neurosurgical Intervention" = noquote(summary$"Neurosurgical Intervention"[2]),
  "External Ventricular Drain" = noquote(summary$"External Ventricular Drain"[2]),
  "Tracheostomy" = noquote(summary$"Tracheostomy"[2]),
  "Days of Mechanical Ventilation" = noquote(summary$"Days of Mechanical Ventilation"[2]),
  "DNR Order" = noquote(summary$"DNR Order"[2]),
  "Withdrawal of Life-Sustaining Therapy" = noquote(summary$"Withdrawal of Life-Sustaining Therapy"[2]),
  "Early Withdrawal of Life-Sustaining Therapy" = noquote(summary$"Early Withdrawal of Life-Sustaining Therapy"[2])
)

table_2

@@

### Sensitivity analysis

>>>>

# gather odds ratios from modelsummary object
odds_ratios <- summary |> map(pluck(1))
odds_ratios[1] <- NULL

# gather credible intervals from modelsummary object
credible_ints <- summary |> map(pluck(2))
credible_ints[1] <- NULL

# gather posterior probabilities of various magnitudes of difference
neurosurgery <- models$"Neurosurgical Intervention" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

evd <- models$"External Ventricular Drain" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

trach <- models$"Tracheostomy" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

vent <- models$"Days of Mechanical Ventilation" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

dnr <- models$"DNR Order" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

wlst <- models$"Withdrawal of Life-Sustaining Therapy" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

early_wlst <- models$"Early Withdrawal of Life-Sustaining Therapy" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

# combine probability of OR > 1 (prob of difference)
prob_difference <- list(
  "Neurosurgical Intervention" = pluck(neurosurgery, 1),
  "External Ventricular Drain" = pluck(evd, 1),
  "Tracheostomy" = pluck(trach, 1),
  "Days of Mechanical Ventilation" = pluck(vent, 1),
  "DNR Order" = pluck(dnr, 1),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 1),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 1)
)

# combine % of posterior within the ROPE
rope <- list(
  "Neurosurgical Intervention" = pluck(neurosurgery, 4),
  "External Ventricular Drain" = pluck(evd, 4),
  "Tracheostomy" = pluck(trach, 4),
  "Days of Mechanical Ventilation" = pluck(vent, 4),
  "DNR Order" = pluck(dnr, 4),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 4),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 4)
)

table1 <- bind_rows(odds_ratios, credible_ints)
table2 <- bind_rows(prob_difference, rope) |> mutate(across(1:7, as.character))

ult_table <- bind_rows(table1, table2)

@@

### Subgroup analyses

### Sensitivity analyses
